Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-23 paper/icml_drau/advup.tex

Contrary to the action state value function,
this
rescaled advantage function converges when $\deltat\to 0$
to an action-dependent quantity which, if it can be learned, contains the
necessary information for policy improvement. A formal statement is given in the supplementary material.

@@

\begin{theorem}
Under suitable smoothness assumptions, $A^\pi_\deltat(s,a)$ has a limit
$A^\pi(s,a)$ when $\deltat\to 0$. The limit keeps information about
actions: namely, if a policy $\pi'$ strictly dominates $\pi$, 
%satisfies $V^{\pi'}>V^{\pi}$ for all states,
then
$A^\pi(s,\pi'(s))>0$ for some state $s$.
\end{theorem}

>>>>

Contrary to the action state value function,
this
rescaled advantage function converges when $\deltat\to 0$
to an action-dependent quantity which, if it can be learned, contains the
necessary information for policy improvement (Thm.~\ref{thm:Alimit}).

@@

\begin{theorem}
\label{thm:Alimit}
Under suitable smoothness assumptions, $A^\pi_\deltat(s,a)$ has a limit
$A^\pi(s,a)$ when $\deltat\to 0$. The limit keeps information about
actions: namely, if a policy $\pi'$ strictly dominates $\pi$, 
%satisfies $V^{\pi'}>V^{\pi}$ for all states,
then
$A^\pi(s,\pi'(s))>0$ for some state $s$.
\end{theorem}
